Type Refinements for the Working Class

### 2015-12-22 paper.tex
fix typo

Before we continue, it makes sense to remark briefly on the strength of the
mathematical foundations that we are assuming for the development of our
framework. As in Martin-L\"of's meaning-theoretic judgmental method, our
apparatus is meant to be understood in a constructive and predicative
metatheory; therefore, by $\Sets$, we do not mean the classical category of
sets, but rather the intuitionistic one, which has lacks the powerset
operation.

>>>>

Before we continue, it makes sense to remark briefly on the strength of the
mathematical foundations that we are assuming for the development of our
framework. As in Martin-L\"of's meaning-theoretic judgmental method, our
apparatus is meant to be understood in a constructive and predicative
metatheory; therefore, by $\Sets$, we do not mean the classical category of
sets, but rather the intuitionistic one, which lacks the powerset
operation.
